% Updated 15 June 2018

\documentclass[12pt]{article}
\begin{document}
\title{Erik H. Beck's Resume}
\author{Erik H. Beck}
\date{15 June, 2018}
\maketitle

\tableofcontents

\setlength{\baselineskip}{10pt}
\section{Applicant Contact Information}

\begin{itemize}
\item
  Erik H. Beck
\item
  150 Rivers Edge Drive, Apartment 213, Medford, MA 02155
\item
  Work Phone: 617-918-1606
\item
  Home Phone: 857-499-9000
\item
  Email: beck.erik@epa.gov, erikbeck@tahoma.com
\end{itemize}

\section{Key Applicable Experience}

\subsection{Management Experience}
\begin{itemize}
\item
  Multiple stints as First Line Supervisor
\item
  Sixteen Months in grade as GS-14 Supervisory Environmental Protection Specialist
\item Determined the overall program goals for all work done in the unit.
\item Oversaw the development of strategies and alternatives to evaluate complex policy issues in the context of the New England environment.
\item Determined office resources needed to accomplish the goals, plans, and requirements of the work unit, and balanced utilization of staff, training needs, and travel budgets.
\item
  Managed extramural resources, both procurement and assistance,
  directly and indirectly.  All contract and assistance resources were
  managed properly, in compliance with statutory and regulatory
  requirements as well as with all EPA policies, procedures, orders,
  and other requirements.
\end{itemize}

\subsection{Contracting, Financial, and Economics Experience}
\begin{itemize}
\item IJC Contract, \$800,000 high visibility
\item Managed multiple millions of dollars for EPA as part of the Lake Champlain geo-program.
\item WA-COR
\item Project Officer for IA and Assistance Agreements
\item BA \& MA in Economics
  
\end{itemize}

\subsection{Information Technology Experience}
\begin{itemize}
\item Is aware of industry standard and EPA specific information security requirements.
\item EPA LAN management experience
\item EPA Power User of all kinds of IT
\item Programming Experience
\item System Administration Experience
\item Using computers since 1979
\item Experience with COOP issues from work with HF SHARES
\item Recommended software and hardware purchases and upgrades (enhancements) for various program offices of EPA
   
\end{itemize}


\section{Full List of Professional Positions}

\subsection {Federal Government}
\subsubsection{Environmental Protection Specialist, Region One,
United States Environmental Protection Agency, U.S. Government}

\begin{itemize}
\item
  2011-present
\item
  GS-028, Grade 13
\item
  Nonpoint Source Coordinator
\item
  Supervises and coordinates the nonpoint source program (CWA 319) in
  New Hampshire.
\item
  Coordinates on the interface between the nonpoint source program and
  the NPDES program at the intersection of stormwater and MS4 permits.
\item
  Evaluates reports and operations of the New Hampshire DES' efforts to
  implement their nonpoint source pollution program.
\item
  Grants Manager
\item
  Awards and manages 319 grants to NHDES and OCFO discretionary grants
  to the University of Southern Maine through the Environmental Finance
  Center program.
\item
  Environmental Finance Coordinator
\item
  Coordinates work of the Environmental Finance Center at the University
  of Southern Maine with work accomplished throughout the region, both
  in and out of EPA.
\item
  NPDES Permits
\item
  Reviews and comments on CAFO permits in Maine.
\item
  Works with lead engineer and others to develop NPDES permits (CWA
  316b) for power plants in New Hampshire.
\item
  Serves as an economics resource for NPDES permitting.
\item
  Information Technology
\item
  Provides hands-on guidance and advice to co-workers.
\item
  Helps regional and national IT staff debug various IT issues.
\item
  Develops outreach materials on new IT initiatives.
\item
  ACS Measures
\item
  For several measures, coordinates EPA strategic measures forecasts and
  actual results and provides reporting on them to stakeholders.
\end{itemize}

\subsubsection{Supervisory Environmental Protection Specialist, Region One, United States Environmental Protection Agency, U.S. Government}

\begin{itemize}
\item
  June 2007-October 2008
\item
  GS-028, Grade 14
\item
  Acting Watersheds and Nonpoint Source Branch Chief
\item
  Supervised a multidisciplinary staff implementing many elements and
  programs of the Clean Water Act, including:
\item
  Watershed planning (CWA 604b) and implementation (Lake Champlain and
  other watersheds);
\item
  The nonpoint source program (CWA 319) across New England;
\item
  Targeted Watershed Grants;
\item
  Promotion of stormwater control systems;
\item
  Development and deployment of decentralized wastewater systems.
\item
  Managed staff workloads and approved time, travel, training, leave,
  and other administrative documents.
\item
  Coordinated and managed the collective negotiation of a complex,
  multimedia funding package (Performance Partnership Agreement) with
  the Vermont Department of Environmental Conservation.
\item
  Supervised project officers managing assistance agreements.
\item
  Tracked budgetary and programmatic progress made by the states in
  several programs, including the PPA and 319 programs.
\item
  Formulated reports of program achievements.
\item
  Duties associated with this temporary promotion were performed
  concurrently with the Lake Champlain Coordinator position discussed
  elsewhere.
\end{itemize}

\subsubsection{Environmental Protection Specialist, Region One,
United States Environmental Protection Agency, U.S. Government}

\begin{itemize}
\item
  2000-2011
\item
  GS-028, Grade 13
\item
  Lake Champlain Coordinator
\item
  Awarded and supervised approximately \$2.5 million annually in grants
  to multiple Lake Champlain entities.
\item
  Managed a highly visible and complex regional, national, and
  international watershed program of implementing the Lake Champlain
  Management Plan.
\item
  Provided technical advice, oversight, and leadership to the Lake
  Champlain Basin Program.
\item
  Tracked environmental, financial, and administrative performance of
  large grant projects to states and other federal agencies.
\item
  Cultivated high level contacts with the U.S. Senate, other federal
  agencies, and state, local, and Canadian provincial agencies.
\item
  Developed and implemented environmental performance benchmarks in a
  collaborative, multi-agency effort.
\item
  Provided expert advice on Lake Champlain grant issues to colleagues
  inside and outside the region.
\item
  Reviewed grant applications for relevancy and quality.
\item
  Negotiated annual multi-media environmental work plans for the State
  of Vermont.
\item
  Chaired Federal Partners for Lake Champlain, supervising a
  multi-agency and multi-disciplinary workgroup to develop environmental
  restoration and outreach programs as well as coordinate federal
  actions implementing the Lake Champlain Management Plan.
\item
  Implemented EPA human resource provisions by hiring and supervising
  interns.
\item
  Coordinated regional response to invasive species issues.
\item
  Worked within a multi-divisional team to respond to petitions and
  lawsuits challenging Vermont's NPDES program and implementation of the
  Lake Champlain TMDL.
\item
  Wrote Op-Ed pieces on invasive species for distribution in newspapers
  throughout New England.
\item
  Led an interagency team to draft policy materials on the impacts of
  ballast water discharge and the means to reduce their ecological risk.
\item
  Served as regional water quality trading contact and resource.
\item
  Used GIS (ESRI) and statistical software (S-Plus) to analyze
  environmental policy issues.
\item
  Served as Co-Chair of the International Joint Commission (IJC)
  Missisquoi Bay Study Board.
\item
  Developed contract under time pressures to carry-out a joint request
  by the US and Canadian Governments to determine the critical sources
  of phosphorus pollution in the international waters of Missisquoi Bay.
\item
  Lead a multi-national effort to supervise the efforts of the
  contractor and the IJC to determine these critical sources.
\item
  Gave presentations to citizens in Canada and the US on the results of
  the IJC efforts in Missisquoi Bay.
\item
  Served as Contracting Officer's Representative (COR) for the IJC
  contract.
\item
  Co-authored final report for an international audience on the IJC work
  in Missisquoi Bay.
\item
  Served as an EPA diver on the Regional Dive Unit during site
  inspections, and managed video documentation of such inspections
  (Adobe Premiere Elements).
\end{itemize}

\subsubsection{Supervisory Environmental Protection Specialist}

\begin{itemize}
\item
  June 2003-October 2003
\item
  Acting Vermont State Unit Chief
\item
  Managed and directed staff of five to carry out the mission of the
  unit.
\item
  Allocated and authorized travel funds and managed staff time and other
  unit resources.
\item
  Reviewed and approved travel, leave, and awards.
\item
  Cultivated unit cooperation and coordination.
\item
  Supported staff by providing technical and administrative advice.
\item
  Coordinated unit, division, and regional efforts on developing a new
  Performance Partnership Agreement with Vermont by forming the PPA
  review team, reviewed and edited all recommendations, and conveyed
  needed changes to Vermont DEC management.
\item
  Served as liaison between staff and upper management, and participated
  in weekly managers meetings.
\item
  Coached staff on job performance and goals in formal (mid-year
  reviews) and informal settings. Reviewed, edited, and approved work
  products.
\item
  Accompanied staff to high visibility outside meetings, and served as
  both a technical and non-technical resource for the work areas.
\item
  Made ``On the Spot'' awards, and recommended staff for other awards
  and accretions.
\item
  Organized the Vermont ``Stormwater Assistance Team (SWAT)'' to respond
  to Vermont's request for help with their precedent-setting stormwater
  docket.
\item Determined the overall program goals for all work done in the unit.
\item Oversaw the development of strategies and alternatives to evaluate complex policy issues in the context of the New England environment.
\item Determined office resources needed to accomplish the goals, plans, and requirements of the work unit, and balanced utilization of staff, training needs, and travel budgets.
\item
  Managed extramural resources, both procurement and assistance,
  directly and indirectly.  All contract and assistance resources were
  managed properly, in complaince with statutory and regulatory
  requirements as well as with all EPA policies, procedures, orders,
  and other requirements.

\end{itemize}

\subsubsection{Environmental Protection Specialist, Region One, United Stated Environmental Protection Agency, U.S.
Government}

\begin{itemize}
\item
  1997-2000
\item
  GS-028, Grade 12
\item
  Vermont Sourcewater Coordinator
\item
  Implemented the Safe Drinking Water Act amendments of 1996,
  particularly the Source Water Assessment and Protection Program
  (SWAP).
\item
  Oversaw development of Vermont's SWAP, coordinated with regional and
  Headquarters specialists, and with Vermont's Water Supply Division.
\item
  Negotiated technical and other details of the program with
  stakeholders in order to reach consensus and a program that met
  statutory and regulatory requirements.
\item
  Communicated technical and general SWAP goals and guidance to
  technical and lay stakeholders.
\item
  Developed strategic plans for Vermont's drinking water program in
  accordance with federal GPRA requirements, and tracked Vermont's
  environmental outcomes and outputs in accordance with these plans.
\item
  Reviewed 305(b) and 303(d) reports.
\item
  Developed GIS expertise (ESRI) and worked with regional and state GIS
  specialists to develop analytical maps.
\item
  Managed 605(b) grant to Vermont.
\item
  Connecticut River Coordinator
\item
  Supported efforts of the Connecticut River Joint Commissions to
  implement the Connecticut River management plan for Vermont and New
  Hampshire.
\item
  Established and coordinated teams for technical and policy
  development.
\item
  Managed grants to state and local agencies.
\item
  Developed GIS map of erosion areas on the Connecticut River in Grafton
  County, New Hampshire.
\item
  Oversaw advisory group to the State of New Hampshire on economics of
  instream flow.
\item
  Authored report on the economics of instream flow.
\end{itemize}

\subsubsection{Environmental Protection Specialist, Headquarters,
Washington DC, United States Environmental Protection Agency, U.S.
Government}

\begin{itemize}
\item
  July 1995-November 1995
\item
  GS-028, Grade 12
\item
  Detailed to HQ from Region Nine.
\item
  Observed economic analysis methods performed in the Economic Analysis
  Branch of the Office of Policy, Planning, and Evaluation.
\item
  Researched and performed reviews of economic survey instruments.
\item
  Provided economic and programmatic insight on permit reform issues.
\item
  Evaluated costs of program conversion from SIC to NAICS.
\end{itemize}

\subsubsection{Environmental Protection Specialist, Region Nine,
Environmental Protection Agency, U.S.
Government}

\begin{itemize}
\item
  1993-1997
\item
  GS-028, Grades 9,11, \& 12
\item
  Air pollution control and permit trading specialist.
\item
  Served as regional contact on several national economic incentive
  program workgroups.
\item
  Participated in the development of RECLAIM, a trading program to
  reduce NOx and SOx from stationary and mobile sources in the Los
  Angeles area.
\item
  Negotiated with stakeholders' staff and managers over many of the
  program's features and details.
\item
  Served as Region Nine's natural resource economist, and provided
  analysis and opinions on the ability of the program and the market to
  function.
\item
  Served as a regional and national expert on control of VOC emissions
  from various stationary and area sources, most notably from personal
  care products.
\item
  Served as divisional PC coordinator and backup LAN administrator.
\item
  Developed, as part of a team, the California Federal Implementation
  Plan under the Clean Air Act.
\end{itemize}


\subsection{Private Sector}

\subsubsection{Boston Smoked Fish Company, Product Demonstration Specialist}
\begin{itemize}
\item
  April, 2017 to present
\item
  Demonstrated smoked fish products at supermarkets and farmers markets
\end{itemize}

\subsubsection{Linux System Administrator}

\begin{itemize}
\item 1999 to 2003
\item
  Installed low-voltage telecom wiring (Ethernet, Telephone, Cable)
\item
  Part-time position
\item
  Established and maintained LAN
\item
  Created network shares
\item
  Established and maintained Internet, phone, and cable TV connectivity
\end{itemize}

\subsubsection{Linux System Administrator; self, family, \&
friends}

\begin{itemize}
\item 1995 to present
\item
  Embedded Systems
\item
  Retrofitted embedded systems with alternative firmware, and managed
  this revised firmware on several different platforms.
\item
  Servers
\item
  Build and managed Linux servers on various Intel and AMD platforms.
\item
  Desktops
\item
  Configured multi-boot systems with various Microsoft products along
  with different Linux distributions (Fedora, OpenSUSE, CentOS).
\item
  System Integration
\item
  Build a network for a small office consisting of many different
  computing environments (Macintosh, Microsoft Windows, Linux) and needs
  (server, desktop, laboratory automation).
\item
  Developed servers to accept, send, and distribute email among the
  various users and machines.
\item
  Adapted servers for file sharing purposes using Samba.
\item
  Built a server for routing packets and packet inspection using
  firewall rules (iptables, ipfilter).
\end{itemize}


\subsubsection{Other Miscellaneous Work
Experience}

\begin{itemize}
\item
  News Paper Carrier, Tacoma News Tribune, 1979-1982
\item
  Dishwasher, Stanley and Seaforts Restaurant, Tacoma Washington. Summer
  1983
\item
  Busboy, Red Robin Restaurant, Seattle, Washington. Spring 1986
\item
  Mobile Ice Cream Sales, Joe's Ice Cream, Seattle, Washington. Spring
  1986
\item
  Special Assistant to the VP, Puget Sound Log Scaling and Grading
  Bureau, Tacoma, Washington. 1983-1985, part-time
\end{itemize}


\subsection {State Government}

\subsubsection{Transportation Analyst, University of Washington \& Washington State Department of Transportation}

\begin{itemize}
\item
  1992-1993
\item
  Led a software development team creating a customized computer program
  for the Washington State Ferry System.
\item
  Wrote software (C++) and documentation, met with onboard testing team
  using the software, and revised program and instructions based on
  feedback.
\item
  Met with WADOT management to negotiate program direction and receive
  feedback on interim and final steps.
\end{itemize}

\subsubsection{Teaching Assistant, University of Washington
Economics
Department}

\begin{itemize}
\item
  Fall 1990
\item
  Taught two sections of \emph{Introduction to Economics}, as part of
  the larger Economics 110 class taught by professor.
\item
  Graded papers and exams.
\item
  Recorded grades.
\item
  Resolved grade disputes.
\item
  Collaborated on writing exams.
\item
  Prepared and delivered lectures.
\end{itemize}

\subsubsection{Research Assistant, University of Washington Economics Department (Seattle Campus)}

\begin{itemize}
\item
  1989-1992 (except fall 1990)
\item
  Devised systems (UNIX, VAX, IBM MVS, PC, NeXT) and wrote software (C,
  PL/1, FORTRAN 77) to prepare very large datasets for statistical
  analysis.
\item
  Performed statistical analysis (SAS).
\item
  Retrieved historic data sets from antique VAX computer systems and
  ported them to modern UNIX systems.
\item
  Condensed all data from dozens of computer reel to reel tapes into
  optical-magnetic drive for NeXT (predecessor of CD-ROM).
\end{itemize}

\subsubsection{Research Assistant, University of Washington School of Oceanography}

\begin{itemize}
\item 1996 to 1989
\item
  Maintained and deployed a benthic flux chamber and box corer in
  shallow and deep marine environments.
\item
  Staffed weeklong and month-long scientific cruises in Hood Canal (WA)
  and the Eastern Pacific Ocean.
\item
  Operated gas chromatograph and interpreted results.
\item
  Devised data entry procedures for preparing historic chromatograph
  results for enhanced analysis.
\item
  Wrote computer programs (BASIC) for shipboard entry of chemical
  parameters of seawater samples.
\item
  Wrote and populated databases for chemical parameters of water
  samples.
\item
  Proofread scientific papers in preparation for submitting to journals.
\end{itemize}

\section {Education}

\subsubsection{Post-Graduate}

\paragraph{Master of Arts in Economics}

\begin{itemize}

\item
  June, 1992
\item
  University of Washington, Seattle, Washington
\item
  Concentration: Natural Resource Economics
\end{itemize}

\subsubsection{Undergraduate}

\paragraph{Bachelor of Arts in Economics}

\begin{itemize}

\item
  June, 1990
\item
  University of Washington, Seattle, Washington
\item
  Unofficial Minors: Chemistry, math, and statistics
\end{itemize}

\paragraph {Miscellaneous Community College}
\begin{itemize}
\item Tacoma Community College
\item Tacoma, Washington
\item Math Course, Fall 1984
\item Typing Course, Summer 1983
\end{itemize}

\subsubsection{Primary and Secondary}

\paragraph {High School}
\begin{itemize}
\item Henry Foss High School
\item Tacoma, Washington
\item September 1982 to June 1985
\item Graduated June, 1985
\end{itemize}

\paragraph {Junior High School}  
\begin{itemize}
\item Hunt Junior High School
\item Tacoma, Washington
\item September 1979 to June 1982
\end{itemize}

\paragraph {Elementary School}

\begin{itemize}
\item John Greenleaf Whittier Elementary
\item Fircrest, Washington
\item Kindergarten through sixth grade
\item September, 1972 to July, 1979
\end{itemize}

\end{document}
